Title

### 2013-03-18 inc/model_results/spacecharge/spacecharge.tex
improve discussion of realistic spacecharge plot

Consider now a simulation comparable to the one presented above, but which uses the initial conditions presented in \ref{eq:summary} and accelerated by an electron gun as modelled in Section \ref{sec:gun_model} which is 20mm in length.
The results of this simulation are presented in \ref{fig:spacecharge_acc}.
\begin{figure}
  \centering
  \begin{tikzpicture}
    \input{spacecharge_data_acc}
  \end{tikzpicture}
  \caption[More realistic free-space pulse evolution vs charge density]{
    The final HW1/eM width (solid) and length (dashed) of pulses which are intially similar except for the number of electrons in the pulse.
    The pulse is generated by 1 mm (HW1/eM) width 1 ps laser pulses with 0.5eV excess photoemission energy.
    It then traverses a 15cm column, a 20mm acceleration region followed by drift region.
  }
  \label{fig:spacecharge_acc}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{tikzpicture}
    \input{spacecharge_data_acc}
  \end{tikzpicture}
  \caption[More realistic free-space pulse evolution vs charge density]{
    The final HW1/eM width (solid) and length (dashed) of pulses which are intially similar except for the number of electrons in the pulse.
    The pulse is generated by 1 mm (HW1/eM) width 1 ps laser pulses with 0.5eV excess photoemission energy.
    It then traverses a 15cm column, a 20mm acceleration region followed by drift region.
  }
  \label{fig:spacecharge_acc}
\end{figure}

Consider now a simulation comparable to the one presented above, but which uses the initial conditions presented in \ref{eq:summary} and accelerated by an electron gun as modelled in Section \ref{sec:gun_model} which is 20mm in length.
The results of this simulation are presented in \ref{fig:spacecharge_acc}.
It is immediately obvious that the final transverse width is larger than in the ideal case presented in \ref{fig:spacecharge_noacc}, even in the low charge-density regime; this is primarily due to the additional divergence imparted by the negative lensing at the anode (see Section \ref{sec:gun_model}).
One can see that though the pulse size does increase beyond a certain total pulse charge, and while that trend appears to start at a higher charge-density, due to the complexity of the pulse dynamics it is rather difficult to compare the exact charge-density from this plot.
What can be seen is that the transverse size increases more sharply with pulse charge at higher levels.
Since the pulse is already diverging in the transverse direction, this is compounded by the increased pulse charge.
This divergence then lowers the overall charge-density more quickly and thus the longitudinal width is not affected as strongly as was seen in \ref{fig:spacecharge_noacc}.
